CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
Generic hypothesis implemented

\subsection{Breast Cancer Wisconsin} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant. We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e. a 0-1 Loss score of 0.75) on our un-shuffled data. We think that the shuffled breast cancer data will be no more than 3\% less accurate.
\subsection{Glass} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps. We hypothesize that we will achieve no less that 65\% accuracy (0-1 Loss of 0.65) for the un-shuffled data, given that there are 7 potential classes. The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.
\subsection{Iris} This data set is comprised of 4 quantitative variables. Each data example can be classified as one of three different flower types. We are predicting approximately 75\% (0-1 Loss of 0.75) accuracy.
\subsection{Soybean} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers. We hypothesize 70\% accuracy (0-1 Loss of 0.7) for this un-shuffled data. For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.
\subsection{Voting Records} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat. We are hypothesizing approximately 85\% accuracy (0-1 Loss of 0.85) for this dataset. We are predicting that the shuffled voting-record data should no more than 3\% less accurate than the shuffled data.\\

>>>>

\subsection{Breast Cancer Wisconsin} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Glass} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Iris} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Soybean} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$

\subsection{Voting Records} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
$H_0 : \mu \geq m$
